A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 main.tex

\begin{figure}
    \caption{Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x $ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x)$, and a number of trials, $n$, where the subscripts $t,i$ refer to the respective value for either the train and test sets.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Optimise $\theta$} according to some method (e.g Eq.~\ref{eq:sgd}).
    \State Record Training Time, $ T_t[i] $
    \State \textbf{Model Inference:} Compute $ \hat{y_i} = K(x_i, \theta) $
    \State Record Inference Time $ T_i[i] $
    \State \textbf{Benign Accuracy:} Calculate $\lambda_{ben}[i]$ using Eq.~\ref{eq:acc}
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}
    \State Record attack generation time, $T_a[i]$
    \State \textbf{Model Inference:} Compute $ y' = K(x_a, \theta) $
    \State \textbf{Adversarial Accuracy:} Calculate $\lambda_{adv}[i]$ with Eq.~\ref{eq:acc}
    \State \textbf{Append} accuracies and times to their respective arrays.
    \EndWhile
    \State \textbf{Fit Accelerated Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
    \State \textbf{Fit Benign Model, $S_{ben}$} using $\lambda_{ben}$ and $T_i$
    \Ensure$ S_{adv} \approx  \phi S_{ben}(\phi t)$
    \Return $S_{adv}$
\end{algorithmic}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
    \caption{Experimental Pipeline Diagram}
    \label{fig:experiments}
\end{figure}

@@

\subsection{Comparative Risk}
\cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice. The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
\[
    \textrm{Comparative~Risk} := \frac{\% \Delta S(t)}{\% \Delta C_a},
\]
where $\% \Delta$ reflects the percent change from the control model.}

@@

For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}. We used three optimisation criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Fig.~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack. Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time. The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost})

@@

\subsection{Survival Analysis}
In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the funciton, $S(t)$. We attempted adding dummy variables for hardware (\textit{e.g.}, peak power and peak bandwidth) as well as the datasets (\textit{e.g.}, resolution, bit depth, and number of color channels), but each of these were strongly co-linear with training time and hindered modelling. As such, they were not included. To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}. We also compared the chosen modelling functions (see Section~\ref{afr}).  These results can be found in Section~\ref{results}.

@@

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=.7\textwidth,clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure*}

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=0.7\textwidth,clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure*}

@@

\begin{figure*}
    \centering
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure*}

\subsection{AFR Models}
\cm{TODO: add 1. fitted parameters and 2. their statistical significance here. Discuss what that means. Move table here. Discuss why we chose Log-Logistic. Discuss accelerated failure assumption again.}

Table~\ref{tab:Combined} shows that the aft models using log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render the plots due to its marginally improved AIC.

\input{plots/combined/aft_comparison}

\cm{Figure TODO shows the p-values for each of the covariates}

Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, that and increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time. Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.

% \begin{figure}
%   \centering
%   % include first image
%   \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
%   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
%   \label{fig:partial_effect_train_time}
% \end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}  
  \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_attack_eps}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_epochs_partial_effect.pdf} 
  \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
  \label{fig:partial_effect_epochs}
\end{figure}

\begin{figure}
  \centering
  % include second image
  \includegraphics[width=0.8\linewidth,trim={20pt 20pt 20pt 20pt},clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf} 
  \caption{TODO: replace this with epochs and batch size}
  \label{fig:partial_effect_batch_size}
\end{figure}

>>>>

\begin{figure}[h!]
    \caption{\textbf{Algorithm: }Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x $ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x)$, and a number of trials, $n$, where the subscripts $t,i$ refer to the respective value for either the train and test sets.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Optimise $\theta$} according to some method (e.g Eq.~\ref{eq:sgd}).
    \State Record Training Time, $ T_t[i] $
    \State \textbf{Model Inference:} Compute $ \hat{y_i} = K(x_i, \theta) $
    \State Record Inference Time $ T_i[i] $
    \State \textbf{Benign Accuracy:} Calculate $\lambda_{ben}[i]$ using Eq.~\ref{eq:acc}
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}
    \State Record attack generation time, $T_a[i]$
    \State \textbf{Model Inference:} Compute $ y' = K(x_a, \theta) $
    \State \textbf{Adversarial Accuracy:} Calculate $\lambda_{adv}[i]$ with Eq.~\ref{eq:acc}
    \State \textbf{Append} accuracies and times to their respective arrays.
    \EndWhile
    \State \textbf{Fit Accelerated Model, $S_{adv}$} using $\lambda_{adv}$ and $T_a$
    \State \textbf{Fit Benign Model, $S_{ben}$} using $\lambda_{ben}$ and $T_i$
    \Ensure$ S_{adv} \approx  \phi S_{ben}(\phi t)$
    \Return $S_{adv}$
\end{algorithmic}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.35\textwidth]{plots/experiment.pdf}
    \caption{Experimental Pipeline Diagram}
    \label{fig:experiments}
\end{figure}

@@

\subsection{Marginal Risk}
\cm{One advantage of this survival analysis is that we can directly compare the marginal risk and reward for a particular model choice. The \textit{marginal risk} is the change in survival time divided by change in attack compared to some control model such that:
\[
    \textrm{Comparative~Risk} := \frac{ \Delta S(t)}{\Delta C_a},
\]
where $\Delta$ reflects the change from the control model.}

@@

For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds ~\cite{legriel2010approximating}. We used three optimisation criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Fig.~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack. Using these values, we fit an AFR model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device. The inference time and training time were used to conduct the cost analysis outlined in the next section (Sec.~\ref{cost}).

@@

\subsection{Survival Analysis}
In addition to the optimisation criteria of benign/adversarial accuracy and training time, we collected prediction times, attack times, power consumption, batch size and number of epochs to be used as covariates of the function, $S(t)$. To fit the AFR model and to plot the effect of covariates, we used the \texttt{lifelines} Python package~\cite{lifelines}. We also compared the chosen modelling functions (see Section~\ref{afr}).  These results can be found in Section~\ref{results}.

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
        \caption{Training, Prediction, and Attack times}
        \label{fig:time}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
        \caption{Training, Prediction, and Attack Power Consumption}
        \label{fig:power}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
        \caption{Training, Prediction, and Attack Monetary Cost}
        \label{fig:cost}
    \end{subfigure}
    \caption{Combined Figures}
\end{figure*}

@@

@@

@@

Table~\ref{tab:Combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}. It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
\input{plots/combined/aft_comparison}

Figure~\ref{fig:partial_effect_train_time} shows that training time, by itself, does little to influence the model's survival time. However, as we see in Fig.~\ref{fig:partial_effect_attack_eps}, increasing the attack distance ($\varepsilon$) by an order of magnitude only marginally reduces the survival time (y-axis). Additionally, that the benign accuracy, Fig.~\ref{fig:partial_effect_accuracy}, is an equally poor indicator of adversarial robustness, raising further concerns about the efficacy of the train/test split methodology.

% \begin{figure}
%   \centering
%   % include first image
%   \includegraphics[width=0.8\linewidth,clip]{plots/combined/log_logistic_train_time_partial_effect.pdf}  
%   \caption{The partial effect of the training time on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
%   \label{fig:partial_effect_train_time}
% \end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
        \caption{Coefficients of the Covariates}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_batch_size_partial_effect.pdf}
        \caption{Batch Size Partial Effect}
    \end{subfigure}
    \caption{This shows the partial effects plots for}
\end{figure}

%   \caption{The partial effect of the attack distance on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
%   \label{fig:partial_effect_attack_eps}
% \end{figure}

% \begin{figure}
%   \centering
%   % include second image
%   \begin{subfigure}

%   \end{subfigure}
%   \caption{The partial effect of the accuracy on the survival time across all datasets and models according to the function $S(t)$ as outlined in Section~\ref{survival_time}. The dotted line represents the baseline survival function $S_{ben}$.}
%   \label{fig:partial_effect_epochs}
% \end{figure}

% \begin{figure}
%   \centering
%   % include second image

%   \caption{TODO: replace this with epochs and batch size}
%   \label{fig:partial_effect_batch_size}
% \end{figure}
